---
title: "Car Model based on MPG"
author: "Guillermo Polanco Serra"
date: "3/24/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Dataset

The data in *mtcars* was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

```{r, echo=TRUE}
head(mtcars)
```

## Sniny App

```{r, echo=FALSE}
library(shiny)

ui <- shinyUI(fluidPage(

    # Application title
    titlePanel("Select desired mpg to obtain a list of cars that fit mpg"),

    # Sidebar with a slider input for number of bins
    sidebarLayout(
        sidebarPanel(
            sliderInput("mpg",
                        "Desired mpg:",
                        min = 10,
                        max = 34,
                        value = 25)
        ),

        # Show a table of the cars matching mpg and cyl
        mainPanel(
            dataTableOutput("table"),
            'Cars with mpg +/- 10% of desired mpg with details'
        )
    )
))

server <- shinyServer(function(input, output) {
  mtcars <- cbind(rownames(mtcars), data.frame(mtcars, row.names=NULL))
  names(mtcars)[names(mtcars) == "rownames(mtcars)"] <- "Model"
    output$table <- renderDataTable({
        # generate table limters from main mtcars dataframe
      min.mpg <- input$mpg - input$mpg*0.1
      max.mpg <- input$mpg + input$mpg*0.1
        # subset table with inputted mpg +/- 10% 
      subset(mtcars, mpg >=min.mpg & mpg <=max.mpg)
    })

})

shinyApp(ui = ui, server = server)
```

## Shiny App (cont)
- Determine the ideal models for a person based on their desired mpg 
- Provides accurate information regarding diverse models that fit within the person's interest

## Future steps
- Add additional data to database
- Provide more options to refine search
- Include each model's price to aid in search